NEXT STEPS:
- Talk about study for non-video services (BRIEFLY): then discuss cons and tHEN add before "... the previous examples all show..."

Apache Flume is distributed, reliable, and available service for efficiently collecting,
aggregating, and moving massive amounts of streaming data from different
applications/webservers into Hadoop Distributed File System (HDFS)(Apache
flume.June, 2015).

Storm is a free and open source distributed real time computational system that does
analysis on streams of data as they come in. The current version 1.0.0 has been
developed since late 2010, and was open-sourced in September 2011 by Twitter, and
then became a top-level project in Apache later by 2014 (Wingerath et al., 2016). It
also simplifies working with queries and workers

Spark streaming is an extension of Spark that is an in-memory distributed data
analysis platform. The spark framework is also often referred as unofficial successor
of Hadoop (Zaharia, Chowdhury, Franklin, Shenker, \& Stoica, 2010), with better and
more concise API resulting in less extravagant application logic and significant
performance improvements through in-memory caching.

Apache Flink is an open source framework for distributed stream processing that
delivers accurate result, even if the data is out of order or has arrived late. In other
words, it is an open source system for processing streaming and batch data. The philosophy behind analytics, batch processing, machine learning, graph analysis, etc., can be stated and achieved as pipelined fault- tolerant data flows (Carbone et al.,2015).

Kafka streams, compared with other streaming engines, are relatively new. It is fast,
scalable, fault tolerant, and offers high throughput. Mainly, it is used for log
processing. It provides an API similar to messaging system, and allows applications
to consume log events in real time (Kreps, Narkhede, \& Rao, 2011)

According to the International Energy Agency,
72\% of the energy consumed in streaming is attributable to user
devices, 23\% to transmission and 5\% to datacenter-based processing [5]


\textbf{(REF 1 PAGE 8 Bredbandsval (2020, September 9))}
(\textbf{REF 2 PAGE 5 PDF})

In fact, research shows that the carbon footprint of streaming decreased in the last few years \textbf{(REF 3 (PAGE 8))},