\label{sec:introduction}
\section{Introduction}

In today's modern digital landscape, streaming services and video on demand (VOD) has become an ubiquitous part of our daily routine. In fact, research show that, since 2017, only 12\% of the Swedish population exclusively watched traditional TV and in 2019, 22\% of the entire population did not consume content on traditional TV at all \cite{a2020_anvndning}. This data indicates a shift in the way the new and upcoming generations interact with online content and hints at the growing role that VOD will have in the near future. However, the environmental impact  and implications of such a technology, particularly in terms of electricity consumption, remain partly unknown. Reports indicate that the transmission as well as the processing of video content on the internet resulted in 306 million tons of carbon dioxide in 2018, which makes up nearly 1\% of the global greenhouse gas emissions \cite{efoui2019climate}. As data rates increase and internet service offerings improve, it is likely that the question around the carbon footprint of online video streaming will gain importance in the next few years. In fact, research shows that the carbon footprint of streaming decreased in the last few years, which is likely due to an increase in the efficiency of video coding standards as well as other technologies in the encoding, transmission and processing of video content. It is, however, still reasonable to assume that its carbon footprint will likely increase in the next few years as demand increases \cite{kamiya2020carbon}. Additionally, there is a lack of accessible and user-friendly tools and software that provide an insight into the energy consumption of streaming. The objective of this project is to develop a content-based measurement system that monitors electricity usage per content played on streaming platforms. This system will empower streaming providers to gain insights and effectively manage their environmental footprint, fostering a more sustainable approach to streaming.


