\label{sec:related_work}

\section{Related Work}
In data streaming analytics applications, there are very few products available on the market, each presenting their own benefits and disadvantages for different use-cases in the industry such as online learning or sports streaming. Each data analytical system is usually accompanied with other services such as video encoding, hosting and delivery. Firstly, one of the most popular products in the market is \textbf{api.video} \footnote{api.video: https://api.video/}, which is a service that allows users to collect real-time play event data for live streams and videos and display them. However, the data collected is shallow and limited to the client's attributes such as the device type, the operating system, browser and approximate location. In-depth analytics, such as power consumption, are not available and other data aggregations are not performed. However, these aspects should not be ignored as research indicates that the client-side energy consumption is indeed the most significant. In fact, the International Energy Agency reports that consumer devices account for 72\% of the energy used for streaming \cite{kamiya2020carbon}. 

Secondly, in terms of applications that are not limited to video streaming but any kind of data streams, there exist many products and frameworks that offer this service such as Apache Flume, Spark streaming, Storm, Apache Flink, Kafka streams and many others. Qualitative research highlights the fact that these applications and frameworks are difficult to operate and expensive, leaving customers not satisfied with the product \cite{chimariya2018streaming}. 

The previous examples all show that there is a market gap for a simple solution that allows the streaming provider to get a better overview of the environmental impact they are having. Such a system is also useful for research such as testing the efficiency of different adaptive bitrate streaming (ABR) algorithms and, therefore, would be targeted at the researchers as opposed to consumers. 
